Fast processing of JUNGFRAU data with the Alpaka library

### 2020-03-02 Publication/manuscript.tex

{\bf Keywords:} Photon pixel detector, fast data processing, GPU programming, Alpaka \textcolor{magenta}{...}

@@

\textcolor{magenta}{
\textbf{requirements:}
\begin{itemize}
	\item real-time data processing (at least 1 detector at 2.5 kHz)
	\item simple and extensible design(?)
	\item portable to other architectures (CPU OpenMP, TBB, ...) with minimal code changes
\end{itemize}
optional requirements:
\begin{itemize}
	\item easily adaptable to similar detectors (e.g. MÖNCH)
\end{itemize}
expected bottlenecks:
\begin{itemize}
	\item communication speed between host and GPU
	\item RAM speed
\end{itemize}
\textbf{design overview:}
\begin{itemize}
	\item wrap for most important alpaka functions (for ease of use) --$>$ explain alpaka shortly (?)
	\item templated for maximal performance and configurability (?)
	\item written in modern C++ for optimal performance
	\item pipelined stream processing of data: upload data to GPU -$>$ process -$>$ download again
	\item multiple detectors and multiple GPUs usable in parallel
\end{itemize}
$<$insert data flow diagram here$>$ \\
architecture specific optimizations:
\begin{itemize}
	\item contiguous memory vs. grid striding loop
	\item only upload data if needed
\end{itemize}
\textbf{software architecture:}
\textit{hardware accelerator concept}
\begin{itemize}
	\item host
	\item device
	\item memory not necessarily shared
	\item data might need to be copied onto device
	\item device starts (possibly asynchronous) execution
	\item result is copied back to host
	\item common host: CPU
	\item common devices: GPUs, FPGAs, Multicore CPUs (in general multi- and manycore systems)
\end{itemize}
$<$insert hardware sketch here$>$
\textit{the dispenser}
\begin{itemize}
	\item handles devices (initialization, memory management, etc.)
	\item enqueues data to next free devices (asynchronously)
	\item copies data back from devices (asynchronously)
\end{itemize}
$<$insert dispenser structure here$>$
\textit{the kernel structure}
\begin{itemize}
	\item written in empty struct as static function
	\item all needed values passed to function, no real access to member variables
	\item most data passed by pointer, only single numbers passed directly
	\item kernel has access to device properties (block size, grid size, device specific functions, etc.)
\end{itemize}
$<$insert example here$>$
\textit{easy hardware abstraction}
\begin{itemize}
	\item useful settings defined for every possible device class
	\item device is selected by using statement (similar to a typedef)
	\item no additional changes needed
\end{itemize}
$<$insert example here$>$
}

>>>>

{\bf Keywords:} Photon pixel detector, fast data processing, GPU programming, Alpaka...

@@

requirements:
 - realtime data processing (at least 1 detector at 2.5 kHz)
 - simple and extensible design
 - portable to other architectures (CPU OpenMP, TBB, ...) with minimal code changes

optional requirements:
 - easily adaptable to similar detectors (e.g. MÖNCH)

design overview:
 - wrap for most important alpaka functions (for ease of use)
 - templated for maximal performance and configurability
 - stream processing of data: upload data to GPU -> process -> download again
 - multiple detectors and multiple GPUs usable in parallel
